Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-04 _02_filtering_data.Rmd

```{r}
# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
```

@@

```{r echo=FALSE}
# wrap plot
figure_01 <-
  wrap_plots(
    fig_filter_bounds,
    fig_outlier_remove
  )+
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
  theme(plot.tag = element_text(face = "bold"))

>>>>

```{r}
# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] <- "seagreen"
```

@@

```{r echo=FALSE}
# wrap plot
figure_01 <-
  wrap_plots(
    fig_filter_bounds,
    fig_outlier_remove
  ) +
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
    theme(plot.tag = element_text(face = "bold"))

### 2021-02-04 _03_smoothing_tracks.Rmd

# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
```

@@

```{r echo=FALSE}
# prepare data
data_agg_smooth = copy(list_of_agg[[3]]) # 30s aggregate
### plot figures
fig_agg_data_smooth <-
      ggplot(data_agg_smooth) +
        geom_point(
          data = data_agg,
          size = 0.2,
          aes(x, y),
          col = pal[3]
        ) +
        geom_path(aes(x, y),
          col = pal[4],
          lwd = 0.2
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 0,
        size = 2,
        col = pal[4],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank()
        ) +
        coord_cartesian(ylim = c(0.6, NA))
```

@@

```{r echo=FALSE}
# prepare data
data_agg_error = copy(list_of_agg_errors[[3]]) # 30s aggregate
### plot figures
fig_agg_data_error <-
      ggplot(data_agg_error) +
        geom_point(
          data = data_errors,
          size = 0.1,
          aes(x, y),
          col = "grey"
        ) +
        geom_path(aes(x, y),
          col = pal[4]
          # lwd = 0.1
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 0,
        size = 2,
        col = pal[4],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank()
        ) +
        coord_cartesian(ylim = c(0.6, NA))
```

@@

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBC"
  )+
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
  theme(plot.tag = element_text(face = "bold"))

>>>>

# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] <- "seagreen"
```

@@

```{r echo=FALSE}
# prepare data
data_agg_smooth <- copy(list_of_agg[[3]]) # 30s aggregate
### plot figures
fig_agg_data_smooth <-
  ggplot(data_agg_smooth) +
  geom_point(
    data = data_agg,
    size = 0.2,
    aes(x, y),
    col = pal[3]
  ) +
  geom_path(aes(x, y),
    col = pal[4],
    lwd = 0.2
  ) +
  geom_point(aes(x, y,
    group = interval
  ),
  shape = 0,
  size = 2,
  col = pal[4],
  alpha = 1,
  show.legend = F
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_cartesian(ylim = c(0.6, NA))
```

@@

```{r echo=FALSE}
# prepare data
data_agg_error <- copy(list_of_agg_errors[[3]]) # 30s aggregate
### plot figures
fig_agg_data_error <-
  ggplot(data_agg_error) +
  geom_point(
    data = data_errors,
    size = 0.1,
    aes(x, y),
    col = "grey"
  ) +
  geom_path(aes(x, y),
    col = pal[4]
    # lwd = 0.1
  ) +
  geom_point(aes(x, y,
    group = interval
  ),
  shape = 0,
  size = 2,
  col = pal[4],
  alpha = 1,
  show.legend = F
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_cartesian(ylim = c(0.6, NA))
```

@@

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBC"
  ) +
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
    theme(plot.tag = element_text(face = "bold"))
